---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# deckhand2

<!-- badges: start -->
```{r}
usethis::use_lifecycle_badge("experimental")
usethis::use_cran_badge()
```
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/deckhand2)](https://CRAN.R-project.org/package=deckhand2)
<!-- badges: end -->

`{deckhand2}` is an extension to the `{pagedown}` package that uses the CSS grid
layout module to provide extensive layout control of page based R Markdown
reports, such as when creating slide decks.

## In development
This package is currently under development and not yet ready for general use.
You can track general progress in the lead [GH issue](https://github.com/mattkerlogue/deckhand2/issues/1).

## History, purpose & acknoweldgements

`{deckhand2}` is a generalised successor to the `{deckhand}` package that I
developed when working at the Cabinet Office. Individuals working in other
institutions have started to use that package, forking it and making relevant
adaptations for their own organisational set-up. Thus {deckhand2} is intended
as a successor to the {deckhand} that provides a more generalised approach for
working with CSS grid-layout and the underlying paged media framework provided
by {pagedown}.


